\documentclass[a4paper,10pt]{article}

\usepackage{url}
\usepackage{parskip} 	
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.86]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\newcolumntype{C}{>{\centering\arraybackslash}X} 
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

\begin{document}
\pagestyle{empty} 

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{\textbf{HIMANSHU}} \\[7.5pt]
\href{https://github.com/waitasecant}{\raisebox{-0.05\height}\faGithub\ waitasecant} \ $|$ \ 
\href{https://linkedin.com/in/waitasecant}{\raisebox{-0.05\height}\faLinkedin\ waitasecant} \ $|$ \ 
\href{https://waitasecant.github.io}{\raisebox{-0.05\height}\faGlobe \ waitasecant.github.io} \ $|$ \ 
\href{mailto:waitasecant@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ waitasecant@gmail.com} \\
\end{tabularx}

% Summary
\section{Summary}
A \textbf{Machine Learning Engineer} with strong foundation in \textbf{Mathematics}, \textbf{Statistics}, and \textbf{Machine Learning} with hands-on experience building \textbf{agentic applications} and a knack for problem solving and attention to detail.

% Work Experience
\section{Work Experience}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{HP Inc. $\mid$ Machine Learning Engineer} & \hfill \textbf{Jun'25 - Present} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item \textbf{Leadership:} Owned development of a python library providing Authorization Middleware for python microservices.
        \item \textbf{Enablement:} Built end-to-end agentic references using Strands, LangGraph, Google ADK implementing several orchestration patterns with A2A and MCP integration ensuring parity across implementations.
        \item \textbf{Initiative:} Contributed to infra pipeline templates enabling pre/post deployment evaluation hook for agents.
        \item \textbf{Development:} Developed an Agent with guardrails, memory, multi-turn, session persistence and authorization assisting with project registration, provisioning LLM models converting weeks' effort into minutes.
    \end{itemize}
    \end{minipage}
}  \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Roni Analytics LLP $\mid$ Data Analyst Intern} & \hfill \textbf{May'24 - Aug'24} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item \textbf{Implemented} production-grade cron jobs to quantify granular \& token level \textbf{TVL} for Pendle \& Kelp protocols.
        \item \textbf{Migrated} the \textbf{on-chain data pipelines} to \textbf{Dune}, \textbf{validated} using \textbf{DelfiLlama} ensuring data integrity.
        \item \textbf{Implemented} multi-threaded \textbf{websocket} solution to track and process \textbf{Bybit} order and tradebooks data to compute granular volume metrics for bid-ask and buy-sell analysis for spot and futures trading.
    \end{itemize}
    \end{minipage}
}  \\
\end{tabularx}

% Projects
\section{Project}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{NavAssist} & \hfill \href{https://github.com/waitasecant/nav-assist}{\textbf{GitHub}} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item \textbf{Core:} An offline edge nav system linking mobile sensing, local inference, and real-time voice and haptic guidance.
        \item \textbf{Tech:} Go WebSocket backend, Android USB camera streaming, YOLOv8-nano ONNX, MiDaS depth, IMU fall detection, and YAMNet audio events unified in a low-latency local pipeline for real-time hazard detection and alerts.
        \item \textbf{Observability:} Prometheus metrics, Grafana dashboard for latency, event traceability and session-level analysis.
    \end{itemize}
    \end{minipage}
}  \\
\end{tabularx}

% \begin{tabularx}{\linewidth}{ @{}l r@{} }
% \textbf{NavAssist} & \hfill \href{https://github.com/waitasecant/nav-assist}{\textbf{GitHub}} \\[3.75pt]
% \multicolumn{2}{@{}X@{}}{\begin{minipage}[t]{\linewidth}
%     \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
%         \item \textbf{Core:} An offline edge nav system linking mobile sensing, local inference, and real-time voice and haptic guidance.
%         \item \textbf{Observability:} Prometheus metrics, Grafana dashboard for latency, event traceability and session-level analysis.
%     \end{itemize}
%     \end{minipage}
% }  \\
% \end{tabularx}

% SKILLS
\section{Skills}

\begin{tabularx}{\linewidth}{ @{}l@{\quad $\mid$} @{\quad}X@{} }
\textbf{Languages \& Cloud} & Python, Go, R, SQL, Azure DevOps  \hfill {}\\
\textbf{ML, Agents \& MLOps} & PyTorch, LangGraph, Strands, MCP, A2A, MLFlow, DVC, Langfuse \hfill {}\\
\textbf{Observability \& Dev Tools} & Git, Docker, OpenTelemetry, Datadog, Grafana, Prometheus \hfill {}
\end{tabularx}

%Hackathons
\section{Open Source, Blog \& Hackathon}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\multicolumn{2}{@{}X@{}}{\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item \textbf{Open Source:} Contributed to \textbf{fraymio/modis-tools} and \textbf{strands-agents/harness-sdk} \hfill \href{https://waitasecant.github.io/open-source/}{\textbf{PRs}}
        \item \textbf{Blog:} Techincal writings on Agents, Evals, ML, Statistics and everything in between. \hfill \href{https://waitasecant.github.io/blog/}{\textbf{Blog}}
        \item \textbf{AmEx Campus Challenge 2024-Decision Track:} Ranked 4 in the Economics/Statistics cohort.
    \end{itemize}
    \end{minipage}
}  \\
\end{tabularx}

% Education
\section{Education}

\begin{tabularx}{\linewidth}{@{}l@{\qquad $\mid$} @{\qquad}l@{\qquad $\mid$} @{\qquad }c@{\qquad $\mid$} @{\qquad}>{\raggedright\arraybackslash}X@{}}
\textbf{Chennai Mathematical Institute} & M.Sc. Data Science & 7.91 & \textbf{2023--25}\\[3pt]
\textbf{Indian Statistical Institute} & PG Diploma in Applied Statistics & 7.00 & \textbf{2023--24}\\[3pt]
\textbf{Institute of Chemical Technology} & M.Sc. Engg. Mathematics & 8.46 & \textbf{2021--23}\\[3pt]
\textbf{Sri Venkateswara College, DU} & B.Sc. (Hons.) Mathematics & 8.29 & \textbf{2018--21}
\end{tabularx}
\end{document}